### 2016-03-21 thesis/abstract.tex
comments on chapters incorporated

Supermassive black holes in the local Universe obey a surprisingly large number of scaling laws 
that involve the black hole mass and various properties of the host spheroids. 
These ``black hole mass scaling relations'' reveal a strong symbiosis between galaxies and black holes, 
define important constraints about their co-evolution through the cosmic time, 
and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution.

A careful galaxy decomposition is required to accurately measure a galaxy's spheroid properties. 
Recent studies have performed structural decomposition 
for similar samples of galaxies with a direct measure of the black hole mass, 
but they have not converged to the same conclusions. 
This is because their best-fit model parameters for the same galaxy were often significantly different 
due to various systematic effects, 
and their models for the same galaxy were frequently not consistent with each other in terms of fitted components. 
Moreover, none of these studies attempted an individual galaxy-by-galaxy comparison of their models 
with the previous literature. 
We have now made this comparison, identified the optimal decomposition, 
and obtained improved black hole mass scaling relations.

Using \emph{Spitzer} observations at $3.6 ~\mu \rm m$, 
which is the best available wavelength band to trace the stellar mass, 
we performed state-of-the-art structural decompositions for $66$ galaxies 
with a direct measure of their black hole mass. 
Thanks to a meticulous inspection of each galaxy's substructure -- 
through photometric and isophotal analysis, unsharp masking, auxiliary information extracted from the literature, 
and, for the first time, kinematic maps, 
we are able to identify \emph{a priori} the physical galaxy components. 
Our multicomponent models account for spheroid, large-scale disc, 
embedded or nuclear discs, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
The combination of photometric and kinematic information was crucial 
to confirm the presence of rotationally supported components in most early-type (elliptical+lenticular) galaxies, 
and to identify their radial extent (nuclear, intermediate-scale or large-scale discs). 
Upon performing galaxy decompositions with both one-dimensional (1D) and two-dimensional (2D) parametric techniques, 
we observed no systematic differences between the results from 1D and 2D methods, 
but we found more advantages in the former.

%Our black hole mass range spans 5 orders of magnitude and allows us to explore the less studied low-mass end of the correlations. 
%We use Spitzer/IRAC 3.6  mosaics because the 3.6  luminosity is the best tracer of the stellar mass.

We confirm that S\'ersic and core-S\'ersic galaxies follow different trends and therefore are associated to different evolutionary scenarios.

We present updates and modifications to several key black hole mass scaling relations, 
and discuss the important implications for galaxy evolution models.

Unlike previous studies that mainly investigated high-mass, early-type galaxies, 
our sample contains a large number of spiral galaxies with low black hole masses ($<10^7 M$), 
and allows us to better investigate the poorly studied low-mass end of the black hole scaling relations.
We present updates and modifications to several key black hole mass scaling relations, showing that early-type (elliptical+lenticular) 
and late-type (spiral) galaxies follow different trends and thus their black holes grow at a different pace, 
and we discuss the important implications for galaxy evolution models.

>>>>

Supermassive black holes in the local Universe obey a surprisingly large number of scaling laws 
that involve the black hole mass and various properties of the host spheroids. 
These ``black hole mass scaling relations'' reveal a strong symbiosis between galaxies and black holes, 
define important constraints about their co-evolution through the cosmic time, 
and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution. \\

%%A careful galaxy decomposition is required to accurately measure a galaxy's spheroid properties. 
%%Recent studies have attempted structural decomposition 
%%for similar samples of galaxies with a direct measure of the black hole mass, 
%%but they have not converged to the same conclusions. 
%%This is because their models for the same galaxy were often not consistent with each other in terms of fitted components, 
%%or, even when they used the same model for the same galaxy, they obtained significantly different best-fit parameters 
%%due to various systematic effects.
%%Moreover, none of these studies attempted an individual galaxy-by-galaxy comparison of their models 
%%with the previous literature. 
%%We have now made this comparison, identified the optimal decomposition, 
%%and obtained improved black hole mass scaling relations, 
%%which are detailed in this thesis. \\

Using \emph{Spitzer} observations at $3.6 ~\mu \rm m$, 
which is the best available wavelength band to trace the stellar mass, 
we performed state-of-the-art structural decompositions for $66$ galaxies 
with a direct measure of their black hole mass. 
Thanks to a meticulous inspection of each galaxy's substructure -- 
through photometric and isophotal analysis, unsharp masking, auxiliary information extracted from the literature, 
and, for the first time, kinematic maps -- 
we were able to identify \emph{a priori} the physical galaxy components. 
%Our multicomponent models account for spheroid, large-scale disc, 
%embedded or nuclear discs, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
The combination of photometric and kinematic information was crucial 
to confirm the presence of rotationally supported components in most early-type (elliptical+lenticular) galaxies, 
and to identify their radial extent (nuclear, intermediate-scale or large-scale discs). 
Upon performing galaxy decompositions with both one-dimensional (1D) and two-dimensional (2D) parametric techniques, 
we observed no systematic differences between the results from 1D and 2D methods, 
but we found more advantages in the former. 
Our 66 galaxies constitute the largest sample to date 
for which these two conditions are satisfied: 
(\emph{i}) the spheroid structural parameters have been measured accurately and homogeneously;  
(\emph{ii}) and the black hole mass has been securely estimated with a direct method. 
%Unlike previous studies that mainly investigated massive early-type galaxies, 
%our sample contains a large number of spiral galaxies with low black hole masses ($<10^7 \rm~M_\odot$), 
%and allowed us to better investigate the poorly studied low-mass end of some black hole mass correlations. 
This thesis presents updates and modifications to several black hole mass scaling relations, 
and discusses important implications for galaxy evolution models. \\

mm + mn \\

ubermassive \\

### 2016-03-21 thesis/ellicular.tex
comments on chapters incorporated

Here we focus on five local early-type galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115) 
for which we performed accurate multicomponent decomposition 
with the aid of photometric and kinematic information. 
Our analysis shows that these galaxies all share the same morphological structure: 
a stellar spheroidal component with the same properties (massive, compact, and old) as the high-redshift red nuggets 
and an intermediate-scale stellar disc that remains embedded within the spheroid. 
These five galaxies had their black hole masses estimated with a direct method.  
Four of them had been previously modelled by other studies \citep{rusli2011,vandenbosch2012,walsh2015,yildirim2015}, 
which failed to account for the correct radial extent of the stellar disc 
and consequently underestimated the spheroid luminosity.
This yielded unusually large $M_{\rm BH} / L_{\rm sph}$ ratios.  \\

>>>>

Here we focus on five local early-type galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115) 
for which we performed accurate multicomponent decomposition 
with the aid of photometric and kinematic information. 
Our analysis shows that these galaxies all share the same morphological structure: 
a stellar spheroidal component with the same properties (massive, compact, and old) as the high-redshift red nuggets, 
and an intermediate-scale stellar disc that remains embedded within the spheroid. 
These five galaxies had their black hole masses estimated with a direct method.  
Four of them had been previously modelled by other studies \citep{rusli2011,vandenbosch2012,walsh2015,yildirim2015}, 
which failed to account for the correct radial extent of the stellar disc 
and consequently underestimated the spheroid luminosity.
This yielded unusually large $M_{\rm BH} / L_{\rm sph}$ ratios.  \\

### 2016-03-21 thesis/mn.tex
corrections to chapters
comments on chapters incorporated

While the previous Chapter was dedicated to the study of the relations between 
black hole mass and galaxy or spheroid luminosity, 
in this Chapter we will perform an analogous analysis 
to explore the relation between black hole mass and spheroid S\'ersic index ($M_{\rm BH} - n_{\rm sph}$). 
To address the issue of consistency between galaxy scaling relations 
that was outlined in Chapter \ref{ch:intro}, 
it is mandatory to include also an analysis of the relation between spheroid luminosity 
and spheroid S\'ersic index ($L_{\rm sph} - n_{\rm sph}$). 
The reliability of the uncertainties associated with the S\'ersic index measurements 
obtained from our 1D decompositions 
ensures a robust estimate of the intrinsic scatter in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
which can be compared with that in the $M_{\rm BH} - L_{\rm sph}$ diagram. \\

The remainder of this chapter comprises the peer-reviewed version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation'' 
by G.~A.~D.~Savorgnan,  
accepted for publication in the \emph{The Astrophysical Journal}.

>>>>

While the previous Chapter was dedicated to the study of the relations between 
black hole mass and galaxy or spheroid luminosity, 
in this Chapter we perform an analogous analysis 
to explore the relation between black hole mass and spheroid S\'ersic index ($M_{\rm BH} - n_{\rm sph}$). 
To address the issue of consistency between galaxy scaling relations 
that was outlined in Chapter \ref{ch:intro}, 
it is mandatory to include also an analysis of the relation between spheroid luminosity 
and spheroid S\'ersic index ($L_{\rm sph} - n_{\rm sph}$). 
The reliability of the uncertainties associated with the S\'ersic index measurements 
obtained from our 1D decompositions 
ensures a robust estimate of the intrinsic scatter in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
which can be compared with that in the $M_{\rm BH} - L_{\rm sph}$ diagram. \\

From a physical point of view, the $M_{\rm BH} - n_{\rm sph}$ correlation is interesting because 
the S\'ersic index is a measure of the central radial concentration of stars, 
which dictates the radial distribution of mass within a galaxy's spheroid 
and therefore determines the dynamical response of stars 
as measured through the observable $\sigma_*$ \citep{grahamdriver2007}. \\

The remainder of this Chapter comprises the peer-reviewed version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation'' 
by G.~A.~D.~Savorgnan,  
accepted for publication in the \emph{The Astrophysical Journal}.
